---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# digavaan

The goal of digavaan is to extract information as R data structures from a `lavaan` object.

## Installation

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("asqm/digavaan")
```

**Warning**: `digavaan` will most likely never go to CRAN because it uses internal functions from `lavaan`. This hinders the package as unstable. However, because most of the inner functions that are used in this package are the same used by `lavaan::summary`, unless there's a breaking change (very unlikely with such a mature package) the same information should be stable.

## Example

Using the same example from `lavaan`:

```{r}
library(lavaan)
library(digavaan)

model <- "
    # latent variables
     ind60 =~ x1 + x2 + x3
      dem60 =~ y1 + y2 + y3 + y4
      dem65 =~ y5 + y6 + y7 + y8
    # regressions
      dem60 ~ ind60
      dem65 ~ ind60 + dem60
    # residual covariances
      y1 ~~ y5
      y2 ~~ y4 + y6
      y3 ~~ y7
      y4 ~~ y8
      y6 ~~ y8"

fit <- sem(model, data=PoliticalDemocracy)

# Traditional print
summary(fit)

# Same information but as a data frames
summary_lavaan(fit)
```


